---
title: "Challenge-5"
author: "Dawn Cheung"
date: "`r Sys.Date()`"
output: html_document

runtime: shiny #bc it says input?????? help i am in pain
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse) #not relavent to this qn but for future use
library(shiny) #not relavent to this qn but for future use
x <- 5
shadowing <- function(x = 5) {
  x <- 10
  sprintf("inside: %d",x)
}
shadowing(x)
sprintf("outside: %d",x)
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total <<- 0

total_accumulator <- function(x) {
  total <<- total + x
}


total_accumulator(5)
total_accumulator(10)
total_accumulator(15)



print(total)
#https://stackoverflow.com/questions/1236620/global-variables-in-r
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total <<- 100 #double arrow here for consistency purposes. single will work fine too.
adding_argue <- function(x) {
  total <<- total + x
  return(total)
}
adding_argue(90)
adding_argue(200)
adding_argue(9)

```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
outer_function <- function() {
  x <- 5
  inner_function <- function(){
    print(x)
  }
  #calling inner function
  inner_function()
}

outer_function()

```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(magick)
tiger <- image_read('https://www.sleepeducation.org/images/healthy-sleep-awareness-project/man-asleep-on-desk.jpg?sfvrsn=0')
image_annotate(tiger, "help me im so tired", size = 100, gravity = "southwest", color = "white", boxcolor = "black")
#the tiger is sarcastic pls understand

```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user *inputs a sentence*, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**
ASSUMPTION: in the context of a layman understanding of "characters", punctuation and spaces will not be included. It wouldn't make sense that your communication skill is more advanced if you spam commas/brackets/etc.

```{r, eval=TRUE,echo=TRUE}
textInput("sentence", "input your sentence", value = NULL)
reactive({ 
  sentence <- renderText({input$sentence}) #im not gg pretend to understand this
  #number of words
  new_sen <- gsub("[[:punct:]]","", input$sentence)
  all_words <- unlist(strsplit(new_sen, " "))
  print("NUMBER O' WORDS: ")
  print(length(all_words))
  
  #number of characters
  new_sen <- gsub("[^[:alnum:]]","", input$sentence)
  num_chara <- nchar(unlist(new_sen))
  print("NUMBER O' CHARA: ")
  print(num_chara)
  
  #average word length
  as.vector(all_words)
  helpme <- mean(nchar(all_words))
  print("AVE WORD LENGTH: ")
  print(helpme)
  
  #comm skill level
  if (num_chara > 0) {
    print("great!! you can communicate!!! 5 stars.")
  } else {
    print("hey if you never try you never know. boo no communication skill for you")
  }
}) #the unlist thing turns it into characters. so u can work with the list elements directly


```
<br>