---
title: "Challenge 7"
author: "Dawn Cheung"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

**Palmer Penguins: Plot recreation**
```{r, eval = TRUE, echo = TRUE}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)

#Slides 8 to 18
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
  geom_point() +
  labs(title = "Bill depth & length",
       subtitle = "Dimensions for Adelie, Chinstrap & Gento Penguins",
       x = "Bill depth (mm)", y = "Bill length (mm)",
       color = "Species",
       caption = "Source: Palmer Station LTER / palmerpenguins package") +
  scale_color_viridis_d()

#the names of the 1st few arguments can be omitted
```

**Aesthetic options: colour, shape, size, alpha**
```{r, eval = TRUE, echo = TRUE}
#Slide 22
ggplot(penguins) +
  aes(x = bill_depth_mm, y = bill_length_mm, colour = species) +
  geom_point() +
  scale_colour_viridis_d()

#Slide 23
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = island)) +
  geom_point() +
  scale_colour_viridis_d()
```


**Slides 24-25 will not be evaluated to reduce document size**
```{r, eval = FALSE, echo = TRUE}
#Slide 24
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species)) +
  geom_point() +
  scale_colour_viridis_d()

#Slide 25
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species, size = body_mass_g)) +
  geom_point() +
  scale_colour_viridis_d()
```

```{r, eval = TRUE, echo = TRUE}
#Slide 26
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species, alpha = flipper_length_mm)) +
  geom_point() +
  scale_colour_viridis_d()
```


**Mapping vs. Setting**
```{r, eval = TRUE, echo = TRUE}
#Slide 28
#MAPPING:
ggplot(penguins) +
  aes(x = bill_depth_mm, y = bill_length_mm,
      size = body_mass_g,
      alpha = flipper_length_mm) +
  geom_point() +
  scale_colour_viridis_d()

#SETTING:
ggplot(penguins) +
  aes(x = bill_depth_mm, y = bill_length_mm) +
  geom_point(size = 2, alpha = 0.5) +
  scale_colour_viridis_d()
```

**Faceting**
```{r, eval = TRUE, echo = TRUE}
#Slide 29
ggplot(penguins) +
 aes(x = bill_depth_mm, y = bill_length_mm) + 
 geom_point() +
 facet_grid(species ~ island)
```

**Slides 30-34 will not be evaluated to reduce document size**
```{r, eval = FALSE, echo = TRUE}
#Slide 30
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(species ~ sex)

#Slide 31
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(sex ~ species)

#Slide 32
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_wrap(~ species)

#Slide 33
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_wrap(~ species, ncol = 2)

#Slide 34
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(. ~ species)
```

```{r, eval = TRUE, echo = TRUE}
#Slide 35
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) + geom_point() +
 facet_grid(species ~ sex) +
  scale_color_viridis_d()

#Slide 36
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) + geom_point() +
 facet_grid(species ~ sex) +
  scale_color_viridis_d() +
  guides(color = "none")
```

**VISUALISING NUMERIC VARIABLES**
```{r, eval = TRUE, echo = TRUE}
#Slide 39 & 40
library(openintro)
#glimpse(loans_full_schema)

loans <- loans_full_schema %>%
 select(loan_amount, interest_rate, term, grade, 
 state, annual_income, homeownership, debt_to_income)

glimpse(loans)

```

**Histogramssss**

Eval set to false to reduce document length
```{r, eval = FALSE, echo = TRUE}
#Slide 46 to 47
ggplot(loans, aes(x = loan_amount)) +
 geom_histogram(binwidth = 1000)

#Slide 49
ggplot(loans, aes(x = loan_amount)) +
 geom_histogram(binwidth = 20000)

#Slide 50
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
 labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )

#Slide 51
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000, alpha = 0.5) +
 labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )

#Slide 52
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
 labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans", caption = "money bye bye" ) +
  facet_wrap(~ homeownership, nrow = 3)
```

**Density plot**

Eval set to false to reduce document size
```{r, eval = FALSE, echo = TRUE}
#Slide 53
ggplot(loans, aes(x = loan_amount)) +
 geom_density()

#Slide 54
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 0.5)

#Slide 55
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 1) # adjust = 1 is default bandwidth

#Slide 56
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 5)

#Slide 57
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 5) +
  labs( x = "How Much Money Bye Bye ($)", y = "Density", title = "Amounts of LC loans" )

#Slide 58
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
 geom_density(adjust = 2, alpha = 0.5) +
  labs( x = "How Much Money Bye Bye ($)", y = "Density", title = "Amounts of LC loans" )
```

**BOX PLOTSSSS**


Eval set to false to reduce document size
```{r, eval = FALSE, echo = TRUE}
#Slide 59
ggplot(loans, aes(x = interest_rate)) +
  geom_boxplot()

#Slide 60
ggplot(loans, aes(x = annual_income)) +
  geom_boxplot()

#Slide 61
ggplot(loans, aes(x = interest_rate, y = grade)) +
 geom_boxplot() +
 labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans", subtitle = "by grade of loan")
```

**S C A T T E R   P L O T S**
```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
 geom_point()
```

**HEX PLOT**
```{r, eval = TRUE, echo = TRUE}
library(hexbin)

ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
 geom_hex()

ggplot(loans %>% filter(debt_to_income < 100), 
 aes(x = debt_to_income, y = interest_rate)) +
 geom_hex()
```

**Bar Plot**
```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(x = homeownership)) +
 geom_bar()
```


**Kueh Lapis Bar Plot**
```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(x = homeownership, fill = grade)) +
 geom_bar()
```

**Same Height Kueh Lapis**
```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(x = homeownership, fill = grade)) +
 geom_bar(position = "fill")
```

```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans", subtitle = "and home ownership of lendee")
```

**Violin Plots**
```{r, eval = TRUE, echo = TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
 geom_violin()
```

**Ridge Plots**
```{r, eval = TRUE, echo = TRUE}
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) + 
 geom_density_ridges(alpha = 0.5)
#Auto joint bandwidth of 2360



```