---
title: "Week-6: Code-along"
author: "Dawn Cheung"
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along-6.Rmd file 
<br>

## A. `for` loop
<br>

### 1. Simple `for` loop (Slide #6)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
for (x in c(3, 6, 9)) { #x assumes the value of each element in the vector, and gets printed accordingly
  print(x)
}
```
<br>

### 2. `for` loops structure (Slide #7)
for (value in list_of_values) {
  do something (based on value)
}
```{r, eval=TRUE,echo=TRUE}
# Left-hand side code: for loop for passing values
for (x in 1:8) {
  print(x)
}
```
<br>
for (index in list_of_indices) {
do something (based on INDEX)
}
```{r, eval=TRUE,echo=TRUE}
# Right-hand side code: for loop for passing indices

y <- seq(from=100, to=200, by=5) #hence u get vector y

for (x in 1:8) {
  print(y[x])
}
```
<br>

### 3. Example: find sample means (Slide #*9*)

```{r, eval=TRUE,echo=TRUE}
# 1. determine what to loop over
sample_sizes <- c(5, 10, 15, 20, 25000)

# 2. pre-allocate space to store output (for efficiency)
sample_means <- double(length(sample_sizes))
# for alternatives, see part 4 of code along

for (i in seq_along(sample_sizes)) { #seq_along is like the indexes of the vector. so seq_along(sample_sizes) == 1:length(sample_sizes). so you get consecutive numbers.
  sample_means[[i]] <- mean(rnorm(sample_sizes[[i]])) #slay
}
sample_means
```
<br>

### 4. Alternate ways to pre-allocate space (Slide #12)

```{r, eval=TRUE,echo=TRUE}
# Example 3 for data_type=double
sample_means <- vector("double", length = 5)
sample_means <- double(5)
sample_means <- rep(0, length(sample_sizes)) #rep is replicate

```
<br>

```{r, eval=TRUE,echo=TRUE}
# Initialisation of data_list
#to hold data of different types
data_list <- vector("list", length = 5)
```
<br>

### 5. Review: Vectorized operations (Slide #18)

```{r, eval=TRUE,echo=TRUE}
# Example: bad idea!
# vector with numbers from 7 to 11
a <- 7:11
#vector with numbers from 8 to 12
b <- 8:12

#vector of all zeros of length 5
out <- rep(0L, 5)

for (i in seq_along(a)) {
  out[i] <- a[i] + b[i]
}
```
<br>

```{r, eval=TRUE,echo=TRUE}
# Taking advantage of vectorization
a <- 7:11
b <- 8:12

out <- a + b
out

#since a and b are vectors of the same length, we dont need to iteratively add them
```
<br>

## B. Functionals

### 6. `for` loops vs Functionals (Slides #23 and #24)
no section for slide 21 [rewrite of earlier example by wrapping it in a function]
```{r, eval=TRUE,echo=TRUE}
# Slide 23
sample_sizes <- c(5, 10, 15, 20, 25000)

fsd <- function(sample_sizes) {
  
  #initalize  an empty vector of the same lenth as sample_sizes
  sample_sds <- rep(0, length(sample_sizes))
  
  #compute the sd of each sample
  for (i in seq_along(sample_sizes)) {
    sample_sds[i] <- sd(rnorm(sample_sizes[i]))
  }
}
#Uh oh! You've copied and pasted this code twice

sample_summary <- function(sample_sizes, fun) {
  out <- vector("double", length(sample_sizes))
  for (i in seq_along(sample_sizes)) {
    out[i] <- fun(rnorm(sample_sizes[i])) #so ur parameter of 'fun' can become the function used here (unique to R, how sad)
    }
  return(out)
}
```
<br>

```{r, eval=TRUE,echo=TRUE}
# Slide 24
#Compute mean
sample_summary(sample_sizes, mean)

# Compute median
sample_summary(sample_sizes, median)

# Compute sd
sample_summary(sample_sizes, sd)

```
<br>

## C. `while` loop

### 7. `while` loop (Slides #27)
while(condition) {}
you can always write a for loop as a while loop,
but you cannot write all while loops as for loops
```{r, eval=TRUE,echo=TRUE}
#SLIDE TWENTY-NINE (29)
# Left-hand side code: for loop
for (i in 1:5) {
  print(i)
}
```
<br>

```{r, eval = TRUE,echo=TRUE}
# Right-hand side code: while loop
i <- 1
while (i <= 5) {
  print(i)
  i <- i+1
}
```
<br>


